\documentclass[10pt, letterpaper]{article}

% Required packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.45in]{geometry} % Optimized for single-page density
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{charter} 
\usepackage{fontawesome5}

% Custom colors
\definecolor{primary}{HTML}{000000}
\definecolor{secondary}{HTML}{444444}
\definecolor{linkcolor}{HTML}{0B51C1}

% Hyperref setup
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    filecolor=magenta,      
    urlcolor=linkcolor,
}

% Section formatting - Compact & Professional
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{4pt}

% Custom commands for entries
\newcommand{\resumeEntryHeader}[4]{
    \noindent \textbf{#1} \hfill #2 \\
    \noindent \textit{#3} \hfill \textbf{#4} \\
}

\begin{document}

% Header - Clean & Compact
\begin{center}
     {\Huge \textbf{MANAN RASTOGI}} \\ [2pt]
     \small \textbf{AI Product Engineer | Applied CV, LLM Evaluation, Full-Stack Systems} \\ [4pt]
    \small
    \faPhone\ +91 9548594935 \hspace{8pt}
    \faEnvelope\ \href{mailto:mananrastogi2k8.210@gmail.com}{mananrastogi2k8.210@gmail.com} \hspace{8pt}
    \faLinkedin\ \href{https://www.linkedin.com/in/manan-rastogi-402697288/}{linkedin.com/in/manan-rastogi} \hspace{8pt}
    \faGithub\ \href{https://github.com/xmananrastogi}{github.com/xmananrastogi}
\end{center}

% Education Section
\section{Education}
\resumeEntryHeader{Vellore Institute of Technology (VIT)}{Vellore, India}{B.Tech in Electronics \& Communication Engineering (Biomedical Specialization)}{2024 -- PRESENT}
\begin{itemize}[noitemsep, topsep=2pt]
    \item \textbf{Core Academics:} Digital Signal Processing, Signals \& Systems, Neural Networks, Biomedical Imaging, Embedded Systems, Microprocessors \& Microcontrollers.
\end{itemize}

\vspace{4pt}

\resumeEntryHeader{IIT Madras}{Online, India}{BS in Data Science \& Applications}{2025 -- PRESENT}
\begin{itemize}[noitemsep, topsep=2pt]
    \item \textbf{Core Academics:} Machine Learning Foundations, Statistical Modeling, Algorithmic Design, Business Data Analytics, Programming in Python \& Java.
\end{itemize}

% Technical Expertise
\section{Technical Expertise}
\begin{description}[font=\bfseries, labelsep=1.5em, leftmargin=1.7in, noitemsep, topsep=2pt, itemsep=2pt]
    \item[Applied AI \& Evaluation] Python 3.12, LLM APIs, prompt evaluation, rule-based validation, OpenCV, scikit-image, TrackPy, SciPy, NumPy.
    \item[Web \& Backend] TypeScript, React.js, Three.js (R3F), Framer Motion, Flask, RESTful APIs, Tailwind CSS, Vite.
    \item[ECE \& Embedded] Verilog, C++, digital logic, DSP, embedded systems foundations, microprocessors, hardware-oriented debugging.
    \item[Data \& Tooling] SQLite, MongoDB, Git, Linux Bash, Docker, Vercel, Postman, performance profiling.
\end{description}

% Role Fit
\section{Relevant Fit for AI Tooling \& Embedded AI}
\begin{itemize}[noitemsep, topsep=2pt, itemsep=2pt]
    \item Strong Python engineering foundation with experience converting noisy technical data into deterministic, testable analysis pipelines.
    \item ECE background with coursework in embedded systems, microprocessors, digital logic, DSP, and technical documentation-heavy subjects.
    \item Comfortable evaluating model/tool outputs critically using metrics, failure cases, rule checks, and human-readable reports.
\end{itemize}

% Technical Project Deployments
\section{Technical Project Deployments}

% Project 1 - WoundTrack AI
\noindent \textbf{\href{https://xmananrastogi-woundtrackai.hf.space/}{WoundTrack AI: Applied Computer Vision Pipeline}} \hfill \textbf{2024 -- PRESENT} \\
\textit{Python, OpenCV, Flask} \hfill \href{https://xmananrastogi-woundtrackai.hf.space/}{[Live Demo]}
\begin{itemize}[noitemsep, topsep=2pt, itemsep=2pt]
    \item Engineered a research-grade CV pipeline tracking \textbf{249+ cells} with \textbf{<10 min} processing on consumer hardware, achieving \textbf{28\% higher precision} than industry-standard manual tracking tools like ImageJ.
    \item Implemented deterministic \textbf{Ensemble Segmentation} (Variance + Entropy filtering) and temporal smoothing via 1D Gaussian kernels to reduce microscopic sensor noise from kinetic velocity curves.
    \item Designed custom evaluation metrics including MSD exponents ($\alpha$), wavefront roughness, and fractal-dimension analysis to validate output quality against biological movement patterns.
    \item Built a Flask + SQLite dashboard for batch processing, kinetic visualization, and automated report generation across 800+ frame analysis workloads.
\end{itemize}

\vspace{6pt}

% Project 2 - Modern Portfolio
\noindent \textbf{\href{https://xmananrastogi.github.io/portfolio/}{Interactive 3D Engineering Portfolio}} \hfill \textbf{2024 -- PRESENT} \\
\textit{TypeScript, React, Three.js (R3F), Framer Motion, Tailwind CSS} \hfill \href{https://xmananrastogi.github.io/portfolio/}{[Live Demo]}
\begin{itemize}[noitemsep, topsep=2pt, itemsep=2pt]
    \item Built a portfolio with \textbf{React Three Fiber} 3D background scene featuring floating wireframe geometries, distortion materials, and star fields rendered via WebGL.
    \item Implemented \textbf{Framer Motion} animation system for scroll-triggered section reveals, layout transitions, and interactive micro-animations.
    \item Added \textbf{WCAG accessibility}: skip navigation, focus-visible rings, ARIA labels, keyboard-dismissible intro, screen-reader live regions, and reduced-motion support.
    \item Responsive design with sticky navigation, scroll progress indicator, and lazy-loaded 3D scene to optimize initial paint.
\end{itemize}

\vspace{6pt}

% Project 3 - GSSoC
\noindent \textbf{Editron — Open Source Contributor (GSSoC '26)} \hfill \textbf{2026} \\
\textit{JavaScript, Git, Open Source Workflow}
\begin{itemize}[noitemsep, topsep=2pt, itemsep=2pt]
    \item Contributing to Editron, an open-source code editor, through GirlScript Summer of Code 2026.
    \item Working on code-quality improvements including removing unused import warnings across the codebase.
    \item Following standard open-source contribution workflow: issue triage, fork, feature branch, and pull request.
\end{itemize}

\end{document}
